---
title: "Chapter 7 Workthrough"
author: "Brianna Cabrera"
output: github_document
---

```{r}
library(tidyverse)
```
##7.3.4 Exercises
###1
```{r}
?diamonds
diamonds
```
The x variable is the length in nm, the y variable is the width in nm, and the z variable is the depth in nm. These are all measurments of diamonds. 

###2
```{r}
ggplot(diamonds) +
  geom_histogram(mapping = aes(x = price))
```
There were not many low price diamonds which is not surprising as diamonds are usually expensive.

###3
```{r}
count(filter(diamonds, carat == 0.99))
```
There 23 diamonds that have exactly 0.99 carats.
```{r}
count(filter(diamonds, carat == 1))
```
I think the cause in the difference is due to cut. 

###4 
```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y), binwidth = 0.5) +
  coord_cartesian(ylim = c(0, 50))
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y), binwidth = 0.5) +
  coord_cartesian(xlim = c(0, 50))
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y)) +
  coord_cartesian(ylim = c(0, 50))
```
The binwidth is automatically set at default when it is not set. 

##7.4.1 Exercises
###1
Missing values are removed and a warning message appears on screen when a histogram has missing values. In a bar chart, the missing values are treated like another catgory.

###2
```{r}
?mean
```
`na.rm = TRUE` in `mean()` and `sum()` indicates whether the missing values should be included or not.

##7.5.1.1 Exercises
###1
```{r}
nycflights13::flights %>%
  mutate(
    cancelled = is.na(dep_time),
    sched_hour = sched_dep_time %/% 100,
    sched_min = sched_dep_time %% 100,
    sched_dep_time = sched_hour + sched_min / 60
  ) %>%
  ggplot() +
  geom_boxplot(mapping = aes(y = sched_dep_time, x = cancelled))
```

###2
The variable most important in the diamonds dataset is most important for predicting the price of a diamond.
```{r}
ggplot(diamonds, aes(x = cut, y = carat)) + 
  geom_boxplot()
```
A larger diamond can be sold even when it has a lower quality cut and vice versa.

###3
```{r}
#install.packages("ggstance")
library(ggstance)
```
```{r}
ggplot(data = mpg) +
  geom_boxploth(mapping = aes(y = reorder(class, hwy, FUN = median), x = hwy))
```
The outputs are the same but the inputs are different.

###4
Not sure how to use this code.

###5
```{r}
?geom_violin
```
A compact display of a continuous distribution. It's a mix of a boxplot and a density plot. Violin plots show the probability density of data at differnt values. 

###6
```{r}
#install.packages("ggbeeswarm")
??ggbeeswarm
```

##7.5.2.1 Exercises

###1
```{r}
?geom_tile
```

###2

```{r}
#install.packages("diplyr")
#library(diplyr)
```

###3 
Can't do number 2 so can't answer #3

##7.5.3.1 Exercises

###1

```{r}
?cut_width
```
Both split variables into groups. 

To use these commands, we need to specify the number of groups made with can change the way the graph looks

###2

```{r}
ggplot(diamonds, aes(x = cut_number(price, 10), y = carat)) +
  geom_boxplot() +
  coord_flip() +
  xlab("Price")
```

###3

The distribution of very large diamonds is more variable which is not surprising. Very large diamonds tend to get sold regardless of the cut and clarity and color. 

###4

```{r}
ggplot(diamonds, aes(x = cut_number(carat, 5), y = price, colour = cut)) +
  geom_boxplot()
```

###5

A scatterplot is able to show more values and emphasizes the trend while showing outliers. 

